AFQ-Insight

### 2019-02-09 reports/manuscript/sections/results.tex
Remove comment about Sarica paper

Using data from a previous study of the corticospinal tract profile and ALS\cite{sarica2017corticospinal}, we tested the performance of AFQ-Insight in a classification setting. The previous study predicted ALS status with a mean accuracy of 80\% using a random forest algorithm based on a priori selection of features within the corticospinal tract. \adam{slight caveat here: not really a priori feature selection but rather a feature selection based on a mean decrease gini cutoff that seems a little bit like peaking. But anyway, I don't really want to recapitulate the entire Sarica paper here so perhaps saying a priori feature selection is a good shorthand}. AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering. The results of the classification prediction are shown in Fig~\ref{fig:class-results}.

>>>>

Using data from a previous study of the corticospinal tract profile and ALS\cite{sarica2017corticospinal}, we tested the performance of AFQ-Insight in a classification setting. The previous study predicted ALS status with a mean accuracy of 80\% using a random forest algorithm based on a priori selection of features within the corticospinal tract. AFQ-Insight delivers competitive predictive performance (mean 84\% accuracy, 0.93 ROC AUC) without the need for a priori feature engineering. The results of the classification prediction are shown in Fig~\ref{fig:class-results}.
